Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/competing_bandits.tex
Added a newline break.
fixes to intro and abstract

\documentclass[format=acmsmall, review=false]{acmart}

@@

\newcommand{\HMR}{\term{HMR}}
\newcommand{\HM}{\term{HM}}
% a very useful package for edits and comments, from David Kempe (USC)
%\usepackage{color-edits}
\usepackage{color-edits}  % use this to suppress the package
\addauthor{as}{red}    % as for Alex
\addauthor{ga}{blue}  % ga for Guy
\addauthor{sw}{orange} % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
\setlength{\tabcolsep}{8pt} % Default value: 6pt
\renewcommand{\arraystretch}{1.5} % Default value: 1

@@

\begin{abstract}
  We empirically study the interplay between \textit{exploration} and
  \textit{competition}. Systems that learn from interactions with
  users often engage in \emph{exploration}: making potentially
  suboptimal decisions in order to acquire new information for future
  decisions. However, when multiple systems are competing for
    the same market of users, exploration may hurt a system's
    reputation in the near term, with adverse competitive effects. In particular, a system may enter a ``death spiral", when the short-term reputation cost decreases
    the number of users for the system to learn from, which degrades
    system's performance relative to competition and further decreases
    the market share.

@@

\subfile{content/conclusion}

\bibliographystyle{acm}
\bibliography{refs,bib-abbrv-short,bib-bandits,bib-AGT,bib-slivkins}

>>>>

\documentclass[format=acmsmall, review=true]{acmart}

@@

\newcommand{\HMR}{\term{HMR}}
\newcommand{\HM}{\term{HM}}
% a very useful package for edits and comments, from David Kempe (USC)
%\usepackage{color-edits}
\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}    % as for Alex
\addauthor{ga}{blue}  % ga for Guy
\addauthor{sw}{orange} % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
\setlength{\tabcolsep}{8pt} % Default value: 6pt
\renewcommand{\arraystretch}{1.5} % Default value: 1

@@

\author{Submission 316}

\begin{abstract}
  We empirically study the interplay between \textit{exploration} and
  \textit{competition}. Systems that learn from interactions with
  users often engage in \emph{exploration}: making potentially
  suboptimal decisions in order to acquire new information for future
  decisions. However, when multiple systems are competing for
    the same market of users, exploration may hurt a system's
    reputation in the near term, with adverse competitive effects. In particular, a system may enter a ``death spiral", when the short-term reputation cost decreases
    the number of users for the system to learn from, which degrades the
    system's performance relative to competition and further decreases
    the market share.

@@

\subfile{content/conclusion}
\newpage 
\bibliographystyle{acm}
\bibliography{refs,bib-abbrv-short,bib-bandits,bib-AGT,bib-slivkins}

### 2019-02-14 paper/content/introduction.tex
fixes to intro and abstract

Online platforms routinely deploy A/B tests, and are increasingly adopting  more sophisticated exploration methodologies based on \emph{multi-armed bandits}, a well-known framework for making decisions under uncertainty and trading off exploration and exploitation (making good near-term decisions). While deploying ``better" learning algorithms for exploration would improve performance, this is not necessarily beneficial under competition, even putting aside the deployment/maintenance costs. In particular, excessive experimentation may hurt platform's reputation and decrease market share in the near term. This would leave the learning algorithm with less users to learn from, which may further degrade platform's performance relative to competitors who keep learning and improving from \emph{their} users, and so forth. \asedit{Taken to the extreme, such dynamics may create a ``death spiral" effect when the vast majority of customers eventually switch to the competitors.}

>>>>

Online platforms routinely deploy A/B tests, and are increasingly adopting  more sophisticated exploration methodologies based on \emph{multi-armed bandits}, a well-known framework for making decisions under uncertainty and trading off exploration and exploitation (making good near-term decisions). While deploying ``better" learning algorithms for exploration would improve performance, this is not necessarily beneficial under competition, even putting aside the deployment/maintenance costs. In particular, excessive experimentation may hurt a platform's reputation and decrease its market share in the near term. This would leave the learning algorithm with less users to learn from, which may further degrade the platform's performance relative to competitors who keep learning and improving from \emph{their} users, and so forth. \asedit{Taken to the extreme, such dynamics may create a ``death spiral" effect when the vast majority of customers eventually switch to competitors.}
